Measurement Bias from Address Aliasing

### 2016-05-26 presentation.tex
Move outline back in front
Highlight alias numbers

@@

\begin{itemize}
  \item Identify address aliasing as an underlying explanation for measurement bias.
  \item How aliasing affects dynamic memory allocation.
  \item Benchmark results.
  \item Opportunities to optimize for aliasing.
  %\item Up to 2x speedup.
\end{itemize}

@@

\begin{table}
  \caption{Events with significant correlation to cycle count.\label{tab:loopcorrelation}}
  \pgfplotstabletypeset[
    int detect, % Output whole numbers for counter values
    col sep=comma,
    columns={Performance counter, Median, [index]3, [index]4},
    column type=r,
    font=\footnotesize,
    columns/Performance counter/.style={
      string type, 
      column type=l,
      column type/.add={|}{},
      postproc cell content/.append code={
        \pgfkeysalso{@cell content=\perfctr{##1}}
      }
    },
    every head row/.style={
      output empty row,
      before row={\hline
        Performance counter & Median & Spike 1 & Spike 2 \\
      },
      after row=\hline\hline
    },
    every last row/.style={after row=\hline},
    every last column/.style={column type/.add={}{|}}
  ]{bin/microkernel-comparison-haswell.csv}
\end{table}
\end{frame}

@@

  Same or similar counters found in architectures dating back through Core 2.

>>>>

\begin{itemize}
  \item Background on measurement bias.
  \item Address aliasing in Intel CPUs.
  \item How aliasing affects dynamic memory allocation.
  \item Benchmark results.
  \item Opportunities to optimize by avoiding aliasing.
  %\item Up to 2x speedup.
\end{itemize}

@@

@@

\pgfplotstableset{
  highlightrow/.style={
    postproc cell content/.append code={
     \count0=\pgfplotstablerow
      \advance\count0 by1
      \ifnum\count0=#1
        \pgfkeysalso{@cell content/.add={$\bf}{$}}
      \fi
    }
  }
}

\begin{table}
  \caption{Events with significant correlation to cycle count.\label{tab:loopcorrelation}}
  \pgfplotstabletypeset[
    int detect, % Output whole numbers for counter values
    col sep=comma,
    highlightrow={1},
    columns={Performance counter, Median, [index]3, [index]4},
    column type=r,
    font=\footnotesize,
    columns/Performance counter/.style={
      string type, 
      column type=l,
      column type/.add={|}{},
      postproc cell content/.append code={
        \pgfkeysalso{@cell content=\perfctr{##1}}
      }
    },
    every head row/.style={
      output empty row,
      before row={\hline
        Performance counter & Median & Spike 1 & Spike 2 \\
      },
      after row=\hline\hline
    },
    every last row/.style={after row=\hline},
    every last column/.style={column type/.add={}{|}}
  ]{bin/microkernel-comparison-haswell.csv}
\end{table}
\end{frame}

@@

  Same or similar counters found in architectures dating back to Core 2.
